\section{Chair's Report (Daniel Thomas)}

This has been a reasonable year for the SRCF. Things have kept rolling along.
I accidentally graduated (it seems a traditional thing for SRCF Chairs to do), a 1.5 year term is too long, I have stopped innovating.
Fortunately we have a chance for a change as I will not be standing for the next committee.

\subsection{Events}
The SRCF Committee should organise a number of events over the course of an academic year: Michaelmas is particularly busy with the Freshers Fair, Welcome Social\footnote{not a squash after confusion in previous years when we were thought to be the University Squash Society}, talks to both the Part IA and II CST students about the SRCF. In Lent there is the AGM and potentially the MRT. In Easter there is the Garden Party and sometimes a dinner.


\subsubsection{Easter}

We held a successful Garden Party on the Trinity Hall which was sponsored by OpenMarket (formerly MX Telecom). We had good attendance and an enjoyable time was had. Again a dinner was not organised though we had intended to do so.

\subsubsection{Michalemas}
The Freshers Fair (FF) resulted in some 35 people signing up to receive one email informing them of how to sign up and numerous people were informed of our existence (last year we had over 100 sign ups but we were not as careful to take email addresses). Several people indicated some interest in potentially helping on the committee or as sysadmins but we did not really follow up on that.

Nicholas Tomlinson gave a brief talk at the Part II CST project briefing on how people could use the SRCF for that. I gave (my worst so far) talk at the IA induction lecture. We failed to organise a talk for the IB students on how to use the SRCF for their group projects.

We held a Welcome Social in the Bridgetower room of Trinity Hall (thanks to Malcolm for booking this).

We managed to submit our accounts on time this year (last year we were late) though it was a little tight and slightly stressful when the Proctor's secretary refused our accounts for not being printed on the correct form (but rather on a much better one we have used for the last n years).

\subsubsection{Lent}
No events or meetings have been held so far this term. We should really have organised the AGM, held an executive meeting and run a Machine Room Tour at the beginning of term.

\subsection{Membership}
We had a particularly poor year in terms of October signups and this was not rectified by higher signups in later months.

Membership exceeds 6849 and we have over 2240 users and host over 880 societies (less users and societies than last year).

\subsection{Outlook}
The SRCF will have an increasingly difficult task to remain relevant in the next decade unless it innovates better than we have in the last year. This is mainly because Google and others are breaking into our space by offering software as a service which is easier to use than the SRCF systems. We can still provide much greater flexibility than they ever can so the enthusiast market should remain ours for a good while yet. Fortunately there are many enthusiasts in Cambridge and even Google can't beat us on price.