\section{Financial Report (Ben Millwood)}

Much of the beginning of my tenure as Junior Treasurer was spent sorting
out the forms and signatories and other stuff that the previous
treasurer, having mysteriously disappeared, left in a bit of a mess.
There were some outstanding payments and donations to be cleared up,
too. Suffice to say, that's all now sorted and we don't currently owe
anyone anything, as far as I'm aware.

We've received roughly £336 in donations since I became treasurer. Many
of these have been in thanks for our generosity – e.g. when we increase
quotas or help fix their websites. Some have come fairly unbidden from
alumni following event-related e-mails we send, so we ought to always
remember to remind people how much we need them. There was a minor hitch
when the subdomain switchover rendered our donate button inoperative for
a few months without us noticing. This is now fixed.

We also received income from the sale of the old Cyclone for £120, and
the AlphaServer and tape robot were eventually sold for a less
impressive £1.

Our sponsorship deals fared a little better: OpenMarket sponsored us
£100 for the garden party in May Week, and have offered to double this
for our next party. 

In hardware terms, we've been donated a couple of new servers (by Third Light), and got
rid of a couple of old ones.

Overall, we're currently operating at a loss, although we have
considerable distance to fall before we hit the ground at this rate. The
increased sponsorship ought to help out, but we will need donations to
increase too; I suspect that this is linked to service quality which is
linked to sysadmin shortages, but effective PR is required as well.

\subsection{Summary of accounts}

A summary of the accounts will be circulated on paper at the AGM.

\subsection{Future}

Depreciation looms: our original estimated lifetimes for both our main
server, pip, and the VM cloud servers, have now expired. They're not
actually falling apart as we speak, but future committees would be
prudent to plan for the replacement of both pip and our other hardware,
if it suddenly becomes necessary. There is a sizeable emergency fund for
exactly this purpose, but it's an emergency fund for a reason; we'd be
in a risky position if it all disappeared. Indeed, having now more
hardware than ever before, we may even wish to increase the emergency
fund in case the CUSU server room burns down or something. pip was
originally bought with some help from the societies syndicate, so we may
wish to consider appealing for their assistance again; realistically,
however, this will not cover the price of replacing anything and anyway
is slow and difficult; we once again find ourselves at the mercy of our
donors (\url{https://www.srcf.ucam.org/donate}).

Tasks for a new treasurer in the coming year: firstly, of course, just
ensure the handover is smooth; on the grounds that I might accidentally
graduate, I recommend this is done before the end of this academic year.
Secondly, we currently have two different inventories, one for the
executive and one for the accounts book; at least the latter is not in
good shape and ought to be reformed. I made an effort to make the
accounts more comprehensible back when I was preparing them for
submission, but more work needs to be done, especially in asset tracking
and valuation.

\subsection{Thanks}

Particular thanks are due to CU Yacht Club, Peterhouse JCR, and CU Canoe
Club for donations as societies, to Third Light for their donation of
hardware and to Open Market (formerly MX Telecom) who sponsored our
garden party. Tomas Ostasevicius, "Zebbie", Rubin Xu, Bogdan Roman, and
Jonny Kram all made personal donations too, along with several members
and societies who wished to remain anonymous.
