\documentclass[a4paper, 12pt]{report}

\title{SRCF Chairman's report 2003/2004}
\author{Matthew Johnson}

\begin{document}

\setcounter{secnumdepth}{-1}

\section{Over the year}

Due to a little misunderstanding, and a lot of incompetence, Barclays closed our bank account this time last year. Fortunately, their information was so out of date they sent the cheque to Matthew Garrett, so we could deposit the money in a new bank account. We have opened a new bank account with HSBC who will, we hope, manage things better.

April was a more interesting month. Kern was compromised by a known but un-patched kernel exploit, but due to the attacker's incompetence was quickly discovered and fixed. The SRCF membership reached over 1000 members (and more recently we reached over 1000 active users). We also made sure that all the custom administration code that we use is free software. This will allow us to help projects elsewhere similar to the SRCF

In May, CUSU started recommending the SRCF for all the societies and groups they host, and migrated many of their existing website to kern.

June saw us starting the {\tt webmail.srcf.ucam.org} service via squirrelmail.

Towards the end of July kern was compromised again. This time it was via several machine-specific exploits. Again this was dealt with quickly, although it took the sysadmins and myself a lot longer to sort out this time, and audit the machine for more local security flaws. This task wasn't helped by discovering that our tape drive had died and we had no recent backups. Since then sysadmin procedures have been overhauled and audited, hopefully leaving us less vulnerable. I'd like to thank Matthew Garret and Martin Keegan, as well as myself, for temporarily helping to admin the machine while the regular sysadmins were away over the summer.

In October the Computing Service asked us to reduce the number of pages indexed by their web search engine. Unfortunately this means that user's personal web pages are no longer indexed by web-search.cam.ac.uk. We also installed SSL certificates signed by the free certificate authority cacert.org.

In November we fixed, at least in part, the problems with backups by installing a large hard disk in calypso (the machine which used to be kern), and we now backup user and society data to that machine on a nightly basis.

Last month there were more attacks by a hacker on kern - fortunately this was was noticed in progress, and stopped. We did, however, have some good news. The attacker from last July was caught, and I gave a statement to the police for use in trial (although he is apparently pleading guilty).

\section{Status}

We would like to thank Hanna Wallach and Lauri Ora, who stepped down from being sysadmins this year for their hard work in the past, and also welcome Stephen Murdoch and Ross Church who have been recently appointed as new sysadmins.

The SRCF now has 1479 members, of which 1131 have active accounts, and we host 421 society accounts.

We also now run 2 machines, and have been donated a third by Lauri Ora, which has not yet been put into use.

\end{document}
