\section{Chair's Report}

I was not originally intending to become the Chair of the SRCF this year but when our previous Chair Han-Ley Tang resigned at the beginning of Michaelmas having accidentally graduated I stood for election at the EGM\footnote{There was some additional fail on my part regarding this, enquire at curry if curious.}. I was previously Secretary on the Committee so I can still relate what happened during the whole period of that committee.

\subsection{Events}
The SRCF Committee should organise a number of events over the course of an academic year: Michaelmas is particularly busy with the Freshers Fair, Welcome Social\footnote{not a squash after confusion in previous years when we were thought to be the University Squash Society}, talks to both the Part IA, IB and II CST students about the SRCF and potentially a Machine Room Tour (MRT) though in practice those have happened in Lent term on the last two occasions. In Lent there is the AGM and potentially the MRT. In Easter there is the Garden Party and the `Annual'/Anniversary Dinner.

In terms of events this year went reasonably well with only a few hicups --- for example the `Annual' Dinner though advertised never actually happened, hopefully the next committee will be able to rectify this.


\subsubsection{Easter}
In May we attempted to obtain sponsorship from Bloomberg and Elliott and Richard Whitehouse went to give a presentation but unfortunately we were not successful. Han-Ley also attempted to obtain sponsorship from Accenture but we were again unsuccessful.
We considered seeing whether we could use \url{http://www.alumni.cam.ac.uk/giving/search.php?all=y} to allow people to donate to the SRCF at the suggestion of Kristian Glass (Sysadmin and ex-PR Officer) but it appears no progress was made on our plan to do so.

We held a successful Garden Party on the Trinity Hall Wychfield site which was sponsored by OpenMarket (formerly MX Telecom). As noted previously we failed to organise the dinner we were intending to organise.

\subsubsection{Michalemas}
The Freshers Fair (FF) resulted in some 104 people signing up to receive one email informing them of how to sign up and numerous people were informed of our existence. Many people indicated some interest in potentially helping on the committee or as sysadmins but we did not really follow up on that.

On the evening of the first day of the FF we held our first EGM\footnote{the ability to hold EGMs was added to the constitution the AGM before last (2009)} which had reasonable attendance of 12 people and was followed by curry which was good. Charles Board a fresher NatSci at Trinity Hall was persuaded to stand as Secretary (and is willing to continue in that position onto the next committee) as part of our program for recognising young talent.

One of the people who had his membership terminated under the previous committee had his membership and account reinstated on this committee as per the conditions made on the termination and at his request. Another person remained terminated at his request\footnote{for further details see curry}.

We gave brief talks at the Part II CST project briefing on how people could use the SRCF for that and at the IA induction lecture (where wifi and other transient bugs with the desktop service resulted in my making an amusing fool of myself).

We held a Welcome Social in the Bridgetower room of Trinity Hall (thanks to Malcolm for booking this) which had good attendance and conversation (though that was a little slow to start).

A brief talk was given to the Part IB CST students at their Group Project briefing about how they could use the SRCF for their group project.

We had to cancel the MRT at short notice due to increased security as a result of the occupation of Old Schools by student protests.

We epically failed at submitting our accounts and so may have ended up de-registering as a University Society --- this should have been covered in more detail in the Treasurer's report.

\subsubsection{Lent 2011}
We held a very successful MRT with a large number of people and it was great fun with many amusing stories related which was followed by a visit to the Anchor Pub by a sizeable number of people and more interesting discussions on various topical and technical issues were had before the Anchor closed\footnote{at the antisocially early hour of 23:15}.

\subsection{Membership}
We did not manage to beat our record for October signups this year though we still managed to do better than any previous year excluding the previous year. Sign up rates this year have been slightly lower than the previous year but still fairly high.

Membership exceeds 6267 and we have over 2370 users and host over 890 societies.