\section{Financial Report}

The financial position of the SRCF remains reasonable though a loss was made in the 2009-2010 academic year due to large hardware purchases.
However we did not submit our accounts before the 31\textsp{st} December deadline as this was not done during term\footnote{there were assurances that this was under control}.
It was not possible to complete this process outside of term as since our bank had failed to correctly set up internet banking and since the box containing the bank statements was in the UK while the Junior Treasurer was in Japan.
This meant that it was not possible to sign off to say that we had a particular quantity of money as we could not be sure that our electronic records were correct.
At the beginning of January we owed various people in excess of £1000 (though we had the money to pay them) and had failed to submit our accounts.
We were also missing 8 of our bank statements and had two unopened letters from the bank.

A the beginning of this term Daniel was given the treasurer box and a meeting of the committee voted to give the Chair emergency powers\footnote{These powers expire at the AGM.} to fix the accounts and (if necessary\footnote{we haven't been informed that we de-registered or that we re-registered but if we had de-registered we should now be re-registered}) get us re-registered as a University Society (Elliott was absent and Daniel abstained). The Chair was able to audit the accounts, balance the books and ensure that all the receipts were numbered such that there is a auditable paper trail for all income and expenditure. Fortunately all our accounts were in order if slightly disorganised. The Chair wrote cheques to all those who were owed money by the SRCF and the Treasurer signed them.

Visits to the bank revealed that the signatories on the account were incorrect as some previous committee had incorrectly filled in the Society Mandate form removing the Senior Treasurer and a new form had not been filed after the EGM to add the new Chair as a signatory and remove the old Chair.

Fortunately this should now all have been resolved and our documentation on this has been improved in an effort to prevent this occurring in future.

\subsection{Summary of accounts}

A summary of the accounts will be circulated on paper at the AGM. We made a loss in 2009-2010 and a smaller profit so far in 2010-2011.

\subsection{Future}
Since the SRCF continues to grow and now has more hardware than at any previous point the SRCF will need to increase the size of its insurance fund. Since the SRCF relies on donations donations would be appreciated (\url{https://www.srcf.ucam.org/donate}).
\subsection{Thanks}
Particular thanks are due to CAUV, CUHaH, EBC and Romance.ucam.org for donations as societies, to Third Light for their large donation and to Open Market (formerly MX Telecom) who sponsored our garden party. Annabel Banks, Chris Hinde and various other individuals who wish to remain anonymous have also made donations this year. Kristian Glass and Malcolm Scott have been owed large sums of money for many months by the SRCF over the last year mainly due to our not getting around to writing the cheques and the SRCF is very grateful to them for bearing with us.